### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-c.tex
cannot figure out figure

% Created by tikzDevice version 0.12.6 on 2025-04-14 23:49:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 25.28, 31.76) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.28, 31.76) rectangle (246.94,165.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (136.11, 31.76) -- (136.11,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 25.28, 31.76) rectangle (246.94,165.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.28, 29.01) --
	( 25.28, 31.76);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 80.69, 29.01) --
	( 80.69, 31.76);

\path[draw=drawColor,line width= 0.4pt,line join=round] (136.11, 29.01) --
	(136.11, 31.76);

\path[draw=drawColor,line width= 0.4pt,line join=round] (191.53, 29.01) --
	(191.53, 31.76);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 25.28, 21.30) {0.200};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 80.69, 21.30) {0.225};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (136.11, 21.30) {0.250};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (191.53, 21.30) {0.275};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (136.11,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.72) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.49,127.13) rectangle (103.49,150.66);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 27.49,144.14) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.49,129.63) rectangle ( 35.49,137.63);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] ( 31.49,129.63) -- ( 31.49,137.63);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.99,130.87) {0.25 mg/m$^3$};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2025-04-15 00:28:48
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 38.23, 31.51) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 38.23, 31.51) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01, 37.60);

\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

\path[fill=fillColor] ( 62.31, 37.60) rectangle ( 69.61, 68.10);

\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.91, 37.60);

\path[fill=fillColor] ( 76.91, 37.60) rectangle ( 84.20, 37.60);

\path[fill=fillColor] ( 84.20, 37.60) rectangle ( 91.50, 68.10);

\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80,159.58);

\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);

\path[fill=fillColor] (106.10, 37.60) rectangle (113.40, 37.60);

\path[fill=fillColor] (113.40, 37.60) rectangle (120.69, 37.60);

\path[fill=fillColor] (120.69, 37.60) rectangle (127.99, 37.60);

\path[fill=fillColor] (127.99, 37.60) rectangle (135.29, 37.60);

\path[fill=fillColor] (135.29, 37.60) rectangle (142.59, 37.60);

\path[fill=fillColor] (142.59, 37.60) rectangle (149.88, 37.60);

\path[fill=fillColor] (149.88, 37.60) rectangle (157.18, 37.60);

\path[fill=fillColor] (157.18, 37.60) rectangle (164.48, 37.60);

\path[fill=fillColor] (164.48, 37.60) rectangle (171.78, 37.60);

\path[fill=fillColor] (171.78, 37.60) rectangle (179.08, 37.60);

\path[fill=fillColor] (179.08, 37.60) rectangle (186.37, 37.60);

\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);

\path[fill=fillColor] (193.67, 37.60) rectangle (200.97, 37.60);

\path[fill=fillColor] (200.97, 37.60) rectangle (208.27, 37.60);

\path[fill=fillColor] (208.27, 37.60) rectangle (215.56, 37.60);

\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);

\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);

\path[fill=fillColor] (230.16, 37.60) rectangle (237.46, 37.60);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 62.31, 37.60) rectangle ( 69.61, 68.10);

\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.91, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 76.91, 37.60) rectangle ( 84.20, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 84.20, 37.60) rectangle ( 91.50, 68.10);

\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 68.10);

\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);

\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.40, 37.60);

\path[draw=drawColor,line width= 0.4pt] (113.40, 37.60) rectangle (120.69, 37.60);

\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);

\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 37.60);

\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.59, 37.60);

\path[draw=drawColor,line width= 0.4pt] (142.59, 37.60) rectangle (149.88, 37.60);

\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);

\path[draw=drawColor,line width= 0.4pt] (157.18, 37.60) rectangle (164.48, 37.60);

\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);

\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.08, 37.60);

\path[draw=drawColor,line width= 0.4pt] (179.08, 37.60) rectangle (186.37, 37.60);

\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 37.60);

\path[draw=drawColor,line width= 0.4pt] (193.67, 37.60) rectangle (200.97, 37.60);

\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);

\path[draw=drawColor,line width= 0.4pt] (208.27, 37.60) rectangle (215.56, 37.60);

\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 37.60);

\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16,129.08);

\path[draw=drawColor,line width= 0.4pt] (230.16, 37.60) rectangle (237.46, 37.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.51) -- (120.69,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.23, 31.51) rectangle (246.94,165.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 34.85) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 80.59) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,126.33) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 37.60) --
	( 38.23, 37.60);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 83.34) --
	( 38.23, 83.34);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,129.08) --
	( 38.23,129.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.76) --
	( 47.71, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.76) --
	(106.10, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.76) --
	(164.48, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.76) --
	(222.86, 31.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 47.71, 21.04) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.10, 21.04) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.48, 21.04) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (222.86, 21.04) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.59,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.59) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 42.31,144.09) rectangle (118.31,164.62);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 42.31,158.10) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 42.31,146.59) rectangle ( 50.31,154.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] ( 46.31,146.59) -- ( 46.31,154.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,147.84) {0.25 mg/m$^3$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 42.31,113.06) rectangle (114.22,141.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 42.31,135.07) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 42.31,123.56) rectangle ( 50.31,131.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 42.31,123.56) rectangle ( 50.31,131.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 42.31,115.56) rectangle ( 50.31,123.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] ( 42.81,116.06) rectangle ( 49.81,123.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,124.80) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 52.31,116.80) {Observed};
\end{scope}
\end{tikzpicture}
